Icicle: write once, run once

### 2016-06-04 2016fhpc/section/01-Introduction.tex
ok

\TODO{Touch on related work}

>>>>

This work is related to stream processing languages such as Lucy~\cite{mandel2010lucy} and Streamit~\cite{thies2002streamit}, but without the need for clock or deadlock analyses.
It is also related to continuous queries~\cite{arasu2003cql} where queries produce results as rows are inserted or deleted, except we can compute arbitrary folds and do not support deletion.

Our implementation is available at \url{https://github.com/ambiata/icicle}.

### 2016-06-04 2016fhpc/section/04-Benchmarks.tex
ok

We evaluated Icicle by replacing an R script which ran weekly in production.
This R script works over around three hundred gigabytes of PSV data.
It computes twelve queries over each of the thirty-one input tables, computing 372 queries in total.

@@

>>>>

We evaluated Icicle by replacing an R script which ran weekly in production.
This R script works over around three hundred gigabytes of pipe-separated values (PSV) data.
It computes twelve queries over each of the thirty-one input tables, computing 372 queries in total.

@@

We have been able to achieve such good results by generating parsing code specialised to the schema, and using data-only flattening~\cite{bergstrom2013data} as an efficient representation of structures such as arrays of sum types and tuples.
By using a query plan that is close to a functional language, we are able to apply many standard optimisations such as common subexpression elimination and dead code removal.
